---
title: "Harrells Cindex"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Calling packages

```{r}
setwd("XXXX")
library(survcomp)
library(survival)
library(ggplot2)
library(purrr)
library(tidyverse)
library(dynpred)
source("http://peterhaschke.com/Code/multiplot.R")

```
calling data 
Input file - 
Col 1 - Pat ID
Col2 - status or event
col 3 - time (OS/EFS/PFS)
Col4 and beyond - different parameters to check, usually clinical parameters like mutational status, gender, age and model like very scores and models 
```{r}
# Setup
args <- commandArgs(trailingOnly = TRUE)
datafile2 <- 'Inputfile.csv'
data2<-read_csv(datafile2,col_names = TRUE) #%>% select(1:44,.) %>% filter(.,!(is.na(Pat)))

```


Harrells's c index using the cindex function
```{r}
S1<- cindex(Surv(time, status) ~ S1, data = data2)
S2<- cindex(Surv(time, status) ~ S2, data = data2)
S3<- cindex(Surv(time, status) ~ S3, data = data2)
S4<- cindex(Surv(time, status) ~ S4, data = data2)
S5<- cindex(Surv(time, status) ~ S5, data = data2)
S6<- cindex(Surv(time, status) ~ S6, data = data2)
S7<- cindex(Surv(time, status) ~ S7, data = data2)
rbind(S1,S2,S3,S4,S5,S6,S7)
```

---------------------------------------------------------------------------------------------------------------------------------------
### THE FOLLOWING IS
Function to compute the concordance index for survival or binary class prediction extrapolated using cox regression function

```{r}
res.cox <- coxph(Surv(time, status) ~ S1, data =  data2)
pred <- predict(res.cox, data=data4, type='risk');
concObj <- concordance.index(pred, res.cox$y[,1], res.cox$y[,2], method='noether');
conc <- concObj$c.index
conc_high <- concObj$upper
conc_low <- concObj$lower
pc <- concObj$p.value
ntot <- a$n
conc0 <- a$concordance[1]
names(conc) = c()
  
c1 <- c(conc, conc_low, conc_high)

```

```{r}
res.cox <- coxph(Surv(time, status) ~ S2, data =  data2)
pred <- predict(res.cox, data=data2, type='risk');
concObj <- concordance.index(pred, res.cox$y[,1], res.cox$y[,2], method='noether');
conc <- concObj$c.index
conc_high <- concObj$upper
conc_low <- concObj$lower
pc <- concObj$p.value
ntot <- a$n
conc0 <- a$concordance[1]
names(conc) = c()
  
c2 <- c(conc, conc_low, conc_high)
```

```{r}
res.cox <- coxph(Surv(time, status) ~ S3, data =  data2)
pred <- predict(res.cox, data=data2, type='risk');
concObj <- concordance.index(pred, res.cox$y[,1], res.cox$y[,2], method='noether');
conc <- concObj$c.index
conc_high <- concObj$upper
conc_low <- concObj$lower
pc <- concObj$p.value
ntot <- a$n
conc0 <- a$concordance[1]
names(conc) = c()
  
c3 <- c(conc, conc_low, conc_high)
```

```{r}
res.cox <- coxph(Surv(time, status) ~ S4, data =  data2)
pred <- predict(res.cox, data=data2, type='risk');
concObj <- concordance.index(pred, res.cox$y[,1], res.cox$y[,2], method='noether');
conc <- concObj$c.index
conc_high <- concObj$upper
conc_low <- concObj$lower
pc <- concObj$p.value
ntot <- a$n
conc0 <- a$concordance[1]
names(conc) = c()
  
c4 <- c(conc, conc_low, conc_high)
```

```{r}
res.cox <- coxph(Surv(time, status) ~ S5, data =  data2)
pred <- predict(res.cox, data=data2, type='risk');
concObj <- concordance.index(pred, res.cox$y[,1], res.cox$y[,2], method='noether');
conc <- concObj$c.index
conc_high <- concObj$upper
conc_low <- concObj$lower
pc <- concObj$p.value
ntot <- a$n
conc0 <- a$concordance[1]
names(conc) = c()
  
c5 <- c(conc, conc_low, conc_high)
```

```{r}
res.cox <- coxph(Surv(time, status) ~ S6, data =  data2)
pred <- predict(res.cox, data=data2, type='risk');
concObj <- concordance.index(pred, res.cox$y[,1], res.cox$y[,2], method='noether');
conc <- concObj$c.index
conc_high <- concObj$upper
conc_low <- concObj$lower
pc <- concObj$p.value
ntot <- a$n
conc0 <- a$concordance[1]
names(conc) = c()
  
c6 <- c(conc, conc_low, conc_high)
```

row combine for the final table
```{r}
rbind(c1,c2,c3,c4,c5,c6,c7)
```
