---
title: "KM curve"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Calling packages

```{r}
setwd("XXX")

#library(survcomp)
library(survminer)
library(survival)
library(ggplot2)
library(rms)

source("http://peterhaschke.com/Code/multiplot.R")
library("viridis")    
library(RColorBrewer)

```
calling data 

INPUT FILE - 
Col 1 - Patient ID
Col 2 - Time (OS/PFS/EFS)
Col 3 - Event or status 
Col 4 and beyond all parameters and groups for which you want KM curves 

```{r}
# Setup
args <- commandArgs(trailingOnly = TRUE)

inputfile <- 'Input_KMcurves.csv'

dataread<-read.csv(inputfile, header = TRUE, sep = ",")#,col_names = TRUE) #%>% select(1:44,.) %>%
dataread <- data.frame(dataread)
```

defining a new file 
KM graph for 3 subgroups TYPE 1
```{r}
require("survival")
fit <- survfit(Surv(osman, d01) ~ PARAMETER1, data = dataread)
ggsurvplot(fit, risk.table = TRUE, pval = TRUE, xlim = c(0,30), xlab = "Time in months", ggtheme = theme_bw(), risk.table.y.text.col = T, risk.table.y.text = FALSE, risk.table.height = 0.3, surv.plot.height = 1, fontsize = 4, palette = c("#E69F00","#00AFBB", "#FC4E07"), legend.labs = c("Group1", "Group2","Group3"))
```

KM graph for 3 subgroups TYPE 2
```{r}
require("survival")
fit <- survfit(Surv(osman2,d01) ~ PARAMETER2, data = dataread)
ggsurvplot(fit, risk.table = TRUE, pval = TRUE, xlim = c(0,51), xlab = "Time in months", ggtheme = theme_grey(), risk.table.y.text.col = T, risk.table.y.text = FALSE, risk.table.height = 0.3, surv.plot.height = 1, fontsize = 4, palette = "Set2", risk.table.col = "strata", legend.labs = c("Group1", "Group2","Group3"), conf.int.fill = TRUE)
```


NOTE - Play with the visualization, for example change the hexadecimal colour palette for colours you like
Several palettes are available on R (eg - Viridis), but hexadecimal values for different colours can be found - https://colorbrewer2.org/#type=qualitative&scheme=Accent&n=3
https://www.datanovia.com/en/blog/the-a-z-of-rcolorbrewer-palette/

NOTE2 - remember to change xlim range to your x-axis range
NOTE3 - change ggtheme in accordance to your preference as well
