---
title: "Kmeans clustering"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("XXX")

library("cluster")
library("factoextra")
library("magrittr")
library("tidyr")
library("supclust")
library("ggpubr")
```

INPUT FILE - 
Col 1 - Patient ID 
Col 2 - OS time/PFS/EFS
Col 3 - Event/Status 
Col 4-11 - Clinical parameters 
Col 12-44 (in this case) - Variable list which was protein intensity in this case 
```{r}
# Setup
args <- commandArgs(trailingOnly = TRUE)

inputfile <- 'Inputfile.csv'
dataread<-read.csv(inputfile, header = TRUE, sep = ";")#,col_names = TRUE) #%>% select(1:44,.) %>%
dataread <- data.frame(dataread)

samplelist <- dataread[1]
varlist <- dataread[12:44]
OStime <- as.data.frame(dataread[2])
clusterfile <- cbind(samplelist,varlist)
clusterfile <- data.frame(clusterfile, row.names = 1)
clusterfile2 <- data.frame(clusterfile, row.names = c(1:41))
clusterfile3 <- cbind(OStime,varlist)

```


common distance measures used for assessing similarity between observations
this will give the output of a distance matrix 
```{r}
res.dist <- get_dist(clusterfile2, stand = TRUE, method = "pearson")

fviz_dist(res.dist, 
   gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
```
Best number of clusters 
```{r}
fviz_nbclust(clusterfile2, kmeans, method = "gap_stat")
```
2D PCA Plot
```{r}
set.seed(123)
km.res <- kmeans(clusterfile2, 3, nstart = 25)
# Visualize
library("factoextra")
fviz_cluster(km.res, data = clusterfile2,
             ellipse.type = "convex",
             palette = "jco",
             ggtheme = theme_minimal())
```
Pam cluster plot
```{r}
pam.res <- pam(clusterfile, 3)
# Visualize
fviz_cluster(pam.res)
```


Heirarchial clustering based on euclidean dissimilarity matrix and WARD.D2 method 
Explore different combinations with distance and matrix 
```{r}
# Compute hierarchical clustering
res.hc <- clusterfile %>%
  scale() %>%                    # Scale the data
  dist(method = "euclidean") %>% # Compute dissimilarity matrix
  hclust(method = "ward.D2")     # Compute hierachical clustering

# Visualize using factoextra
# Cut in 4 groups and color by groups
fviz_dend(res.hc, k = 3, # Cut in four groups
          cex = 0.5, # label size
          k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07"),
          color_labels_by_k = TRUE, # color labels by groups
          rect = TRUE # Add rectangle around groups
          )
```
heatmap of the above keeping the dendrogram true
```{r}
heatmap((t(as.matrix(clusterfile2))), keep.dendro = TRUE, cexCol = "0.5", cexRow = "0.5", margins = c(1,1))
```
Fuzzy cluster 
```{r}
res.fanny <- fanny(clusterfile2, 3)
res.fanny$coeff
fviz_cluster(res.fanny, ellipse.type = "norm", repel = TRUE,
             palette = "jco", ggtheme = theme_minimal(),
             legend = "right")
fviz_silhouette(res.fanny, palette = "jco",
                ggtheme = theme_minimal())
```


C-statistic
```{r}
sksurv.metrics.concordance_index_censored(dataread$d01, dataread$osman, dataread$SIG33, tied_tol=1e-08)¶

```

