---
title: "Multivriate Cox regression"
author: "Lavanya Lokhande"
date: "3/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

setting directory
```{r}
setwd("XXX")
```

calling libraries
```{r}
library(survcomp)
library(survival)
library(ggplot2)
library(purrr)
source("http://peterhaschke.com/Code/multiplot.R")
```

INPUT FILE - 
Column 1 - Patient ID
Column 2 - Event or status
Column 3 - Survival time, in the following script it is given as "time"
Column 4 and beyond - all the variables to check for cox
Row represents all samples with Row 1 being the column headers

```{r}
# Setup
args <- commandArgs(trailingOnly = TRUE)

## If you run from the commandline
##datafile <- args[1]

## If you run within R
##datafile <- 'example-data.csv.csv'

datafile <- 'OS_COMBAT_43.csv'

data<-read.table(datafile, header=T, sep=",", dec=".", na.strings = "NA")
## if you problem with calling the file, check the 'sep' in the above line

#
write.table(c(), file="multivariate cox_coxRes.csv", row.names=FALSE, col.names=FALSE)


ID<-data[1]
os<-data[3]
event<- data[2]
time<- as.numeric(as.character(unlist(os[1])))
status<- as.numeric(as.character(unlist(event[1])))
```

for the multivariate cox the calling function is the same, you simply need to call all variables with a "+" 
```{r}
res.cox <- coxph(Surv(time, status) ~ Var1 + Var2 + Var3 + ........, data =  data)

print(summary(res.cox))

#write.delim(data2, append=TRUE, file="multi_coxRes-OS_ComBat-SD.csv", row.names=FALSE, col.names=FALSE)
```

