---
title: "Cox Regression"
author: "Lavanya Lokhande and Mattias Ohlsson"
date: "3/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("XXX") ##Set your directory
```

##Calling libraries
```{r}
library(survcomp)
library(survival)
library(ggplot2)
library(survminer)
source("http://peterhaschke.com/Code/multiplot.R")
```

INPUT FILE - 
Column 1 - Patient ID
Column 2 - Event 
Column 3 - Survival time, in the following script it is given as "Stime1"
Column 4 and beyond - all the variables to check for cox
Row represents all samples with Row 1 being the column headers

```{r}
# Setup
args <- commandArgs(trailingOnly = TRUE)


datafile <- 'Input_file.csv'

data<-read.table(datafile, header=T, sep=",", dec=".", na.strings = "NA")
## if you problem with calling the file, check the 'sep' in the above line

write.table(c(), file="coxRes.csv", row.names=FALSE, col.names=FALSE)
write.table(c(), file="coxCheck.csv", row.names=FALSE, col.names=FALSE)
```

##Cox regression main script 
#final output are the values for concordant index and confidence interval, hazard ratio and CI, pval for HR, Pval for concordant index and coeffifcient values 
```{r}
mysave <- function(xx, num, mode){
  a <- summary(xx)
  # Cindex
  pred <- predict(xx, data=data, type='risk');
  concObj <- concordance.index(pred, xx$y[,1], xx$y[,2], method='noether');
  conc <- concObj$c.index
  conc_high <- concObj$upper
  conc_low <- concObj$lower
  pc <- concObj$p.value 
  
  ntot <- a$n
  conc0 <- a$concordance[1]
  names(conc) = c()
  
  tmp1 <- a$conf.int
  tmp2 <- a$coefficients
  tmp3 <- md$coefficients
  varnames <- names(tmp3)
  print(tmp2)
  #print(conc)
  
  for (i in 1 : num) {
    hr = tmp1[i,1]
    hr_low <- tmp1[i,3]
    hr_high <- tmp1[i,4]
    coeff <- tmp2[i,1]
    pval <- tmp2[i,5] ## for hazard ratio
    vname <- varnames[i]
    
    vals <- c(mode, vname, ntot, conc, conc_low, conc_high, hr, hr_low, hr_high, pval, pc, coeff)
    write.table(t(vals), append=TRUE, file="coxRes.csv", row.names=FALSE, col.names=FALSE)
    #print(vals)
  }
}
```

## defining Cox check function where the proportionality model is tested
## for model to be applicable the output pvalue should be non-significant
```{r}
coxcheck <- function(xx, num, mode){
  cc <- cox.zph(xx)
  #print(cc)
  #plot(cc)
  tmp <- cc$table
  varnames <- rownames(tmp);
  
  for (i in 1 : num) {

    pval <- tmp[i,3]
    vname <- varnames[i]
    
    vals <- c(mode, vname, pval)
    write.table(t(vals), append=TRUE, file="coxCheck.csv", row.names=FALSE, col.names=FALSE)
  }

  #plot.new();
  #if (num > 1) {
  #  par(mfrow=c(2,2))
  #}
  #plot(cc, main=mode);
  
}
```

## calling the above 2 function for your dataset 

```{r}
vl <- names(data)
vl <- vl[-c(1,2,3)]
len <- length(vl)

#########_____________ this part is only if you call for one variable at a time 

#md <- coxph(Surv(Stime1, Event) ~ Var1, data)
#mysave(md, 1, 'U')
#coxcheck(md, 1, 'U')

#md <- coxph(Surv(Stime1, Event) ~ Var2, data)
#mysave(md, 1, 'U')
#coxcheck(md, 1, 'U')
#########_____________



#########_____________ this part is only if you call for many variable at a time i.e. when you have hundreds of variables to check for cox and writing single variable at a time like above is not feasible. this is still a univariate analysis

myplots <- list() 
blist <- list()
for (j in 1:len){
    print(j)
    f1 = as.formula(paste("Surv(Stime1, Event) ~ ", paste(vl[j], collapse="+")))
    md <- coxph(f1, data=data)
    vals1 <- c(vl[j], md[1],md[5])
    write.table(t(vals1), append=TRUE, file="coxcoeff.csv", row.names=FALSE, col.names=FALSE)
    mysave(md, 1, 'U')
    coxcheck(md, 1, 'U')
    ggforest(md)
}
#########_____________
```

## the final output files would be saved in the directory you set in the first step